Data Management for LSST Special Programs

### 2024-04-05 sec_proc.tex
fix typo

\item \textbf{DIA Object histories may become too large for the sizing model.}
Alert packets contain the full records of all associated 
{\tt DiaSources} from the past 12 months, but the alert
stream bandwidth is sized for the expected histories for
Main Survey fields. 
The Prompt pipeline resources are also sized for the
Main Survey, and it might not be possible to load up
thousands of epochs at a time.
The Data Management team will have to test the realized
capabilities of Prompt processing and alert distribtuion,
and potentially impose a mitigation strategy such as
limiting histories to the last $N$ observations instead
of the last 12 months in heavily-observed regions.
Alerts from Special Programs data are subject to the same latency
requirements as Main Survey alerts (Section~\ref{ssec:req_proc}).

>>>>

\item \textbf{DIA Object histories may become too large for the sizing model.}
Alert packets contain the full records of all associated 
{\tt DiaSources} from the past 12 months, but the alert
stream bandwidth is sized for the expected histories for
Main Survey fields. 
The Prompt pipeline resources are also sized for the
Main Survey, and it might not be possible to load up
thousands of epochs at a time.
The Data Management team will have to test the realized
capabilities of Prompt processing and alert distribution,
and potentially impose a mitigation strategy such as
limiting histories to the last $N$ observations instead
of the last 12 months in heavily-observed regions.
Alerts from Special Programs data are subject to the same latency
requirements as Main Survey alerts (Section~\ref{ssec:req_proc}).
